---
title: "NutritionRequirementsInfo"
author: "Ye Shen"
date: "3/31/2022"
output: html_document
---
# README
This document scrapes the DRI tables and then cleans the data for use. It also provides info on energy converter and added sugar limits in plain text.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval=FALSE)
library(rvest)
library(tidyverse)
library(janitor)
```



# Energy converter (The Atwater general factor system)
  * protein: 4 kcal/g
  * fat: 9 kcal/g
  * carbohydrates: 4 kcal/g

Citation: Food and Agriculture Organization of the United Nations (FAO). 2002. Food energy - methods of analysis and conversion factors. FAO FOOD AND NUTRITION PAPER 77. [link] (https://www.fao.org/3/y5022e/y5022e04.htm#fn9)


# Added Sugar
Added sugar came from [Dietary Guideline for Americans 2020-2025] (https://www.dietaryguidelines.gov/sites/default/files/2020-12/Dietary_Guidelines_for_Americans_2020-2025.pdf#page=31) 

The Dietary Guidelines for Americans 2020–2025 recommends Americans 2 years and older keep their intake of added sugars to less than 10% of their total daily calories. Children younger than 2 years should not be fed foods and beverages with added sugars at all.



# Dietary Reference Intakes (DRI)
Tables of Dietary Reference Intakes (DRI) are from [Institute of Medicine](https://ods.od.nih.gov/HealthInformation/Dietary_Reference_Intakes.aspx)

Citation: National Research Council (US) Subcommittee on the Tenth Edition of the Recommended Dietary Allowances. Recommended Dietary Allowances: 10th Edition. Washington (DC): National Academies Press (US); 1989. 3, Energy. Available from: https://www.ncbi.nlm.nih.gov/books/NBK234932/

## Energy
### Average Energy Allowance (kcal)
  * Note: Energy age groups are slightly different from the rest of the DRIs for elements, vitamins, and macronutrients.
```{r}
url_energy<-"https://www.ncbi.nlm.nih.gov/books/NBK234938/table/ttt00007/?report=objectonly"

energy<-url_energy%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__ttt00007_lrgtbl__"]/table')%>%
          html_table()
energy_tb<-energy[[1]]
## write to csv and manually change the group labels rows to one column
write_excel_csv(energy_tb, "energy.csv")
## read in the csv file
energy_tb<-read_csv("energy_manual.csv")
## Setting numeric variables
energy_tb<-energy_tb%>%
              mutate(across(3:8,as.numeric))
saveRDS(energy_tb, "cleaned/energy_final.rds")
energy_tb<-readRDS("cleaned/energy_final.rds")
#filter to household examples demographics manually
write_excel_csv(energy_tb, "NutrReq4HouseholdEx/energy.csv")


```



## Elements
### Recommended Dietary Allowances and Adequate Intakes, Elements
```{r}
## scraping data from the NIH websites
url_elements<-"https://www.ncbi.nlm.nih.gov/books/NBK545442/table/appJ_tab3/?report=objectonly"

elements<-url_elements%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__appJ_tab3_lrgtbl__"]/table')%>%
          html_table()
elements_tb<-elements[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(elements_tb, "elementsRDA.csv")
## read in the csv file
elements_tb<-read_csv("elementsRDA_manual.csv")
## removing characters from cells that should be numbers
remove<-c("\\*","a",",")
elements_tb[-1:-2]<-apply(elements_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))
## Setting numeric variables
elements_tb<-elements_tb%>%
                mutate(across(3:17,as.numeric))
saveRDS(elements_tb, "cleaned/elementsRDA_final.rds")
elements_rda_tb<-readRDS("cleaned/elementsRDA_final.rds")

## filter to household examples demographics and add count variables of household members in example 1, 2, 3, or 4.
elements_rda_tb<-elements_rda_tb%>%
              filter((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="9–13 y")| (Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="19–30 y")| (Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y")| (Group=="Females"&Age=="> 70 y"))%>%
                  mutate(house_1=ifelse((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y"),1,0),
                         house_2=ifelse((Group=="Males"&Age=="9–13 y")|(Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y"),1,0),
                         house_3=ifelse((Group=="Females"&Age=="> 70 y"),1,0),
                         house_4=ifelse((Group=="Males"&Age=="19–30 y")|(Group=="Males"&Age=="19–30 y"), 2,0))

saveRDS(elements_rda_tb, "NutrReq4HouseholdEx/elementsLowerBound_final.rds")
elements_rda_tb<-readRDS( "NutrReq4HouseholdEx/elementsLowerBound_final.rds")
write_excel_csv(elements_rda_tb,"NutrReq4HouseholdEx/elementsLowerBound.csv")

```

### Tolerable Upper Intake Levels, Elements
```{r}
url_elements_uil<-"https://www.ncbi.nlm.nih.gov/books/NBK545442/table/appJ_tab9/?report=objectonly"



elements_uil<-url_elements_uil%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__appJ_tab9_lrgtbl__"]/table')%>%
          html_table()

elements_uil_tb<-elements_uil[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(elements_uil_tb, "elementsUIL.csv")
## read in the csv file
elements_uil_tb<-read_csv("elementsUIL_manual.csv")
## removing characters from cells that should be numbers
elements_uil_tb[-1:-2]<-apply(elements_uil_tb[-1:-2],2,str_remove_all,",")
## coding NAs
elements_uil_tb<-elements_uil_tb%>%
                  mutate(across(.cols = everything(),na_if,"ND"))%>%
                   mutate(across(.cols = everything(),na_if,"NDh"))
## Setting numeric variables
elements_uil_tb<-elements_uil_tb%>%
                mutate(across(3:23,as.numeric))
saveRDS(elements_uil_tb, "cleaned/elementsUIL_final.rds")
elements_uil_tb<-readRDS("cleaned/elementsUIL_final.rds")

## filter to household examples demographics and add count variables of household members in example 1, 2, 3, or 4.
elements_uil_tb<-elements_uil_tb%>%
              filter((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="9–13 y")| (Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="19–30 y")| (Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y")| (Group=="Females"&Age=="> 70 y"))%>%
                  mutate(house_1=ifelse((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y"),1,0),
                         house_2=ifelse((Group=="Males"&Age=="9–13 y")|(Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y"),1,0),
                         house_3=ifelse((Group=="Females"&Age=="> 70 y"),1,0),
                         house_4=ifelse((Group=="Males"&Age=="19–30 y")|(Group=="Males"&Age=="19–30 y"), 2,0))

saveRDS(elements_uil_tb, "NutrReq4HouseholdEx/elementsUpperBound_final.rds")
elements_uil_tb<-readRDS( "NutrReq4HouseholdEx/elementsUpperBound_final.rds")
write_excel_csv(elements_uil_tb,"NutrReq4HouseholdEx/elementsUpperBound.csv")

```

## Vitamins

### Recommended Dietary Allowances and Adequate Intakes, Vitamins
```{r}
url_vitamins<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t2/?report=objectonly"



vitamins<-url_vitamins%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t2_lrgtbl__"]/table')%>%
          html_table()

vitamins_tb<-vitamins[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(vitamins_tb, "vitaminsRDA.csv")
## read in the csv file
vitamins_tb<-read_csv("vitaminsRDA_manual.csv")
## removing characters from cells that should be numbers
remove<-c("\\*",",","h")
vitamins_tb[-1:-2]<-apply(vitamins_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))
## Setting numeric variables
vitamins_tb<-vitamins_tb%>%
                mutate(across(3:16,as.numeric))
saveRDS(vitamins_tb, "cleaned/vitaminsRDA_final.rds")
vitamins_rda_tb<-readRDS("cleaned/vitaminsRDA_final.rds")

## filter to household examples demographics and add count variables of household members in example 1, 2, 3, or 4.
vitamins_rda_tb<-vitamins_rda_tb%>%
              filter((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="9–13 y")| (Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="19–30 y")| (Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y")| (Group=="Females"&Age=="> 70 y"))%>%
                  mutate(house_1=ifelse((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y"),1,0),
                         house_2=ifelse((Group=="Males"&Age=="9–13 y")|(Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y"),1,0),
                         house_3=ifelse((Group=="Females"&Age=="> 70 y"),1,0),
                         house_4=ifelse((Group=="Males"&Age=="19–30 y")|(Group=="Males"&Age=="19–30 y"), 2,0))

saveRDS(vitamins_rda_tb, "NutrReq4HouseholdEx/vitaminsLowerBound_final.rds")
vitamins_rda_tb<-readRDS( "NutrReq4HouseholdEx/vitaminsLowerBound_final.rds")
write_excel_csv(vitamins_rda_tb,"NutrReq4HouseholdEx/vitaminsLowerBound.csv")

```

### Tolerable Upper Intake Levels, Vitamins
```{r}
url_vitamins_uil<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t7/?report=objectonly"



vitamins_uil<-url_vitamins_uil%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t7_lrgtbl__"]/table')%>%
          html_table()

vitamins_uil_tb<-vitamins_uil[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(vitamins_uil_tb, "vitaminsUIL.csv")
## read in the csv file
vitamins_uil_tb<-read_csv("vitaminsUIL_manual.csv")
## removing characters from cells that should be numbers
remove<-c(",","e")
vitamins_uil_tb[-1:-2]<-apply(vitamins_uil_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))

## coding NAs
vitamins_uil_tb<-vitamins_uil_tb%>%
                  mutate(across(.cols = everything(),na_if,"ND"))
## Setting numeric variables
vitamins_uil_tb<-vitamins_uil_tb%>%
                mutate(across(3:17,as.numeric))
saveRDS(vitamins_uil_tb, "cleaned/vitaminsUIL_final.rds")

vitamins_uil_tb<-readRDS("cleaned/vitaminsUIL_final.rds")

## filter to household examples demographics and add count variables of household members in example 1, 2, 3, or 4.
vitamins_uil_tb<-vitamins_uil_tb%>%
              filter((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="9–13 y")| (Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="19–30 y")| (Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y")| (Group=="Females"&Age=="> 70 y"))%>%
                  mutate(house_1=ifelse((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y"),1,0),
                         house_2=ifelse((Group=="Males"&Age=="9–13 y")|(Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y"),1,0),
                         house_3=ifelse((Group=="Females"&Age=="> 70 y"),1,0),
                         house_4=ifelse((Group=="Males"&Age=="19–30 y")|(Group=="Males"&Age=="19–30 y"), 2,0))

saveRDS(vitamins_uil_tb, "NutrReq4HouseholdEx/vitaminsUpperBound_final.rds")
vitamins_uil_tb<-readRDS( "NutrReq4HouseholdEx/vitaminsUpperBound_final.rds")
write_excel_csv(vitamins_uil_tb,"NutrReq4HouseholdEx/vitaminsUpperBound.csv")
```

## Macronutrients
### Recommended Dietary Allowances and Adequate Intakes, Total Water and Macronutrients
```{r}
url_macronutrients<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t4/?report=objectonly"

macronutrients<-url_macronutrients%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t4_lrgtbl__"]/table')%>%
          html_table()

macronutrients_tb<-macronutrients[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(macronutrients_tb, "macronutrientsRDA.csv")
## read in the csv file
macronutrients_tb<-read_csv("macronutrientsRDA_manual.csv")
## removing characters from cells that should be numbers
remove<-c("\\*",",","c")
macronutrients_tb[-1:-2]<-apply(macronutrients_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))
## Setting numeric variables
macronutrients_tb<-macronutrients_tb%>%
                mutate(across(3:8,as.numeric))
saveRDS(macronutrients_tb, "cleaned/macronutrientsRDA_final.rds")
macronutrients_rda_tb<-readRDS("cleaned/macronutrientsRDA_final.rds")
## filter to household examples demographics and add count variables of household members in example 1, 2, 3, or 4.
macronutrients_rda_tb<-macronutrients_rda_tb%>%
              filter((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="9–13 y")| (Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="19–30 y")| (Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y")| (Group=="Females"&Age=="> 70 y"))%>%
                  mutate(house_1=ifelse((Group=="Children"&Age=="4–8 y")|(Group=="Males"&Age=="14–18 y")|(Group=="Males"&Age=="31–50 y")| (Group=="Females"&Age=="9–13 y")|(Group=="Females"&Age=="31–50 y")| (Group=="Females"&Age=="51–70 y"),1,0),
                         house_2=ifelse((Group=="Males"&Age=="9–13 y")|(Group=="Females"&Age=="9–13 y")| (Group=="Females"&Age=="19–30 y"),1,0),
                         house_3=ifelse((Group=="Females"&Age=="> 70 y"),1,0),
                         house_4=ifelse((Group=="Males"&Age=="19–30 y")|(Group=="Males"&Age=="19–30 y"), 2,0))

saveRDS(macronutrients_rda_tb, "NutrReq4HouseholdEx/macronutrientsLowerBound_final.rds")

macronutrients_rda_tb<-readRDS( "NutrReq4HouseholdEx/macronutrientsLowerBound_final.rds")
write_excel_csv(macronutrients_rda_tb,"NutrReq4HouseholdEx/macronutrientsLowerBound.csv")

```

### Acceptable Macronutrient Distribution Ranges (Percent of energy range)
```{r}
url_macronutrients_ar<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t5/?report=objectonly"

macronutrients_ar<-url_macronutrients_ar%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t5_lrgtbl__"]/table')%>%
          html_table()

macronutrients_ar_tb<-macronutrients_ar[[1]][-1,]
macronutrients_ar_tb<-as.tibble(t(macronutrients_ar_tb))%>%
                        janitor::row_to_names(row_number=1)
colnames(macronutrients_ar_tb)[1]<-"Group"

saveRDS(macronutrients_ar_tb, "cleaned/macronutrientsAR_final.rds")
macronutrients_ar_tb<-readRDS("cleaned/macronutrientsAR_final.rds")

write_excel_csv(macronutrients_ar_tb, "NutrReq4HouseholdEx/macronutrientsAR.csv")


```


