---
title: "ScrapedNutritionRequirements"
author: "Ye Shen"
date: "3/31/2022"
output: html_document
---
#README
This document scrapes the DRI tables and then cleans the data for use. In the last section, it also provides info on added sugar limits if we want to use this constraint.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyverse)
library(janitor)
```

Tables of Dietary Reference Intakes (DRI) are from [Institute of Medicine](https://ods.od.nih.gov/HealthInformation/Dietary_Reference_Intakes.aspx)

Added sugar came from [Dietary Guideline for Americans 2020-2025] (https://www.dietaryguidelines.gov/sites/default/files/2020-12/Dietary_Guidelines_for_Americans_2020-2025.pdf#page=31) 

## Elements
### Recommended Dietary Allowances and Adequate Intakes, Elements
```{r}
## scraping data from the NIH websites
url_elements<-"https://www.ncbi.nlm.nih.gov/books/NBK545442/table/appJ_tab3/?report=objectonly"

elements<-url_elements%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__appJ_tab3_lrgtbl__"]/table')%>%
          html_table()
elements_tb<-elements[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(elements_tb, "elementsRDA.csv")
## read in the csv file
elements_tb<-read_csv("elementsRDA_manual.csv")
## removing characters from cells that should be numbers
remove<-c("\\*","a",",")
elements_tb[-1:-2]<-apply(elements_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))
## Setting numeric variables
elements_tb<-elements_tb%>%
                mutate(across(3:17,as.numeric))
saveRDS(elements_tb, "cleaned/elementsRDA_final.rds")
elements_rda_tb<-readRDS("cleaned/elementsRDA_final.rds")


```

### Tolerable Upper Intake Levels, Elements
```{r}
url_elements_uil<-"https://www.ncbi.nlm.nih.gov/books/NBK545442/table/appJ_tab9/?report=objectonly"



elements_uil<-url_elements_uil%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__appJ_tab9_lrgtbl__"]/table')%>%
          html_table()

elements_uil_tb<-elements_uil[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(elements_uil_tb, "elementsUIL.csv")
## read in the csv file
elements_uil_tb<-read_csv("elementsUIL_manual.csv")
## removing characters from cells that should be numbers
elements_uil_tb[-1:-2]<-apply(elements_uil_tb[-1:-2],2,str_remove_all,",")
## coding NAs
elements_uil_tb<-elements_uil_tb%>%
                  mutate(across(.cols = everything(),na_if,"ND"))%>%
                   mutate(across(.cols = everything(),na_if,"NDh"))
## Setting numeric variables
elements_uil_tb<-elements_uil_tb%>%
                mutate(across(3:23,as.numeric))
saveRDS(elements_uil_tb, "cleaned/elementsUIL_final.rds")
```

## Vitamins

### Recommended Dietary Allowances and Adequate Intakes, Vitamins
```{r}
url_vitamins<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t2/?report=objectonly"



vitamins<-url_vitamins%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t2_lrgtbl__"]/table')%>%
          html_table()

vitamins_tb<-vitamins[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(vitamins_tb, "vitaminsRDA.csv")
## read in the csv file
vitamins_tb<-read_csv("vitaminsRDA_manual.csv")
## removing characters from cells that should be numbers
remove<-c("\\*",",","h")
vitamins_tb[-1:-2]<-apply(vitamins_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))
## Setting numeric variables
vitamins_tb<-vitamins_tb%>%
                mutate(across(3:16,as.numeric))
saveRDS(vitamins_tb, "cleaned/vitaminsRDA_final.rds")
vitamins_rda_tb<-readRDS("cleaned/vitaminsRDA_final.rds")

```

### Tolerable Upper Intake Levels, Vitamins
```{r}
url_vitamins_uil<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t7/?report=objectonly"



vitamins_uil<-url_vitamins_uil%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t7_lrgtbl__"]/table')%>%
          html_table()

vitamins_uil_tb<-vitamins_uil[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(vitamins_uil_tb, "vitaminsUIL.csv")
## read in the csv file
vitamins_uil_tb<-read_csv("vitaminsUIL_manual.csv")
## removing characters from cells that should be numbers
remove<-c(",","e")
vitamins_uil_tb[-1:-2]<-apply(vitamins_uil_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))

## coding NAs
vitamins_uil_tb<-vitamins_uil_tb%>%
                  mutate(across(.cols = everything(),na_if,"ND"))
## Setting numeric variables
vitamins_uil_tb<-vitamins_uil_tb%>%
                mutate(across(3:17,as.numeric))
saveRDS(vitamins_uil_tb, "cleaned/vitaminsUIL_final.rds")
```

## Macronutrients
### Recommended Dietary Allowances and Adequate Intakes, Total Water and Macronutrients
```{r}
url_macronutrients<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t4/?report=objectonly"



macronutrients<-url_macronutrients%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t4_lrgtbl__"]/table')%>%
          html_table()

macronutrients_tb<-macronutrients[[1]]

## write to csv and manually change the group labels rows to one column
write_excel_csv(macronutrients_tb, "macronutrientsRDA.csv")
## read in the csv file
macronutrients_tb<-read_csv("macronutrientsRDA_manual.csv")
## removing characters from cells that should be numbers
remove<-c("\\*",",","c")
macronutrients_tb[-1:-2]<-apply(macronutrients_tb[-1:-2],2,str_remove_all,paste(remove,collapse = "|"))
## Setting numeric variables
macronutrients_tb<-macronutrients_tb%>%
                mutate(across(3:8,as.numeric))
saveRDS(macronutrients_tb, "cleaned/macronutrientsRDA_final.rds")
macronutrients_rda_tb<-readRDS("cleaned/macronutrientsRDA_final.rds")
```

### Acceptable Macronutrient Distribution Ranges (Percent of energy range)
```{r}
url_macronutrients_ar<-"https://www.ncbi.nlm.nih.gov/books/NBK56068/table/summarytables.t5/?report=objectonly"

macronutrients_ar<-url_macronutrients_ar%>%
          read_html()%>%
          html_nodes(xpath='//*[@id="__summarytables.t5_lrgtbl__"]/table')%>%
          html_table()

macronutrients_ar_tb<-macronutrients_ar[[1]][-1,]
macronutrients_ar_tb<-as.tibble(t(macronutrients_ar_tb))%>%
                        janitor::row_to_names(row_number=1)
colnames(macronutrients_ar_tb)[1]<-"Group"
saveRDS(macronutrients_ar_tb, "cleaned/macronutrientsAR_final.rds")
macronutrients_ar_tb<-readRDS("cleaned/macronutrientsAR_final.rds")

```

### Added Sugar
The Dietary Guidelines for Americans 2020–2025 recommends Americans 2 years and older keep their intake of added sugars to less than 10% of their total daily calories. Children younger than 2 years should not be fed foods and beverages with added sugars at all.


